\tool: Revisiting BadUSB with Type-C

### 2021-03-07 WOOT/Files/countermeasure.tex
revise contermeasure

\textbf{External Hardware Authorization.} One possible countermeasure is to
introduce external hardware completing the authorization process. Contrary to
the GoodUSB, USBCheckIn~\cite{usbcheckin} adopts a dedicated hardware between
the host and device. When a device is plugged-in, the authorization will be
conducted on the dedicated hardware instead of the internal display, preventing
the host from being hijacked. Though USBCheckIn is an adequate defense against
\tool, the external hardware brings additional cost and inconvenience,
especially for mobile devices.

\textbf{Distrust-by-Default.} Most security issues of \ac{USB} protocol are due to
its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
To defend against \tool and other USB-based attacks, we can simply reject all
{unauthorized} device -- applying the \textit{distrust-by-default} policy.  It
is worth mentioning that \textit{distrust-by-default} policy is not the same as
GoodUSB~\cite{tian2015defending}.  
%\fengwei{the following sentence needs to be
%written. I am confused.}\hongyi{Fixed, use more concise sentences} 
GoodUSB permits limited functionality of untrusted devices while this strict policy forbids all functions of an untrusted device. Though \textit{distrust-by-default} policy effectively
prevents these attacks, it also causes considerable inconvenience for users.

>>>>

\textbf{External Hardware Authorization.} One possible countermeasure is to
introduce external hardware completing the authorization process. For example,
 USBCheckIn~\cite{usbcheckin} adopts a dedicated hardware between
the host and device. When a device is plugged-in, the authorization will be
conducted on the dedicated hardware instead of the internal display, preventing
the host from being hijacked. Though USBCheckIn is an adequate defense against
\tool, the external hardware brings additional cost and inconvenience,
especially for mobile devices.

\textbf{Distrust-by-Default.} Most security issues of \ac{USB} protocol are due to
its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
To defend against \tool and other USB-based attacks, we can simply reject all
{unauthorized} device -- applying the \textit{distrust-by-default} policy. For example, 
in GoodUSB~\cite{tian2015defending}, all \ac{USB} devices are enabled with corresponding 
functionality only after being authorized by the user. This defense effectively stops attack 
like \tool.
